---
title: "PSYC"
author: "Chi Zhang"
date: "07/09/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("psych")
library(car)
```

# Read in the csv file
```{r}
Nego_data <- read.csv(file = "Data with Bio culture and Average Score.csv")
Nego_data
```

# General significant test with linear model and stepwise selection
```{r}
Culture <- Nego_data$Bio_Culture
Dignity <- Nego_data$Dignity
Face <- Nego_data$Face

# linear model and test significance of factors
model <- lm(Culture ~ (Dignity + Face)^2)

# Stepwise selection process and figure out the significant factor(s)
# Only intercept and Dignity factor are significant in this model
model <- step(model)
```

# Only dignity factor is significant
```{r}
# print out the summary table of the reduced model
summary(model)
```

# Assumption test
```{r}
# Done the assumption test
Culture <- as.factor(Culture)
leveneTest(Dignity ~ Culture)
leveneTest(Face ~ Culture)
```

# Descriptive data of face and dignity score for mono & bio culture
```{r}
# Record data into list for mean and SD descriptive data
mono_face_culture <- c()
mono_dig_culture <- c()
bio_face_culture <- c()
bio_dig_culture <- c()

for (i in 1:length(Culture)){
  if (Culture[i] == "1"){
    mono_face_culture <- c(mono_face_culture, Face[i])
    mono_dig_culture <- c(mono_dig_culture, Dignity[i])
  } else{
    bio_face_culture <- c(bio_face_culture, Face[i])
    bio_dig_culture <- c(bio_dig_culture, Dignity[i])
  }
}
```

# SD values
```{r}
# SD value for mono-culture of in face score
sd(mono_face_culture)

# SD value for mono-culture of in dignity score
sd(mono_dig_culture)

# SD value for bio-culture of in face score
sd(bio_face_culture)

# SD value for bio-culture of in dignity score
sd(bio_dig_culture)
```

# Mean values
```{r}
# Mean value for mono-culture of in face score
mean(mono_face_culture)

# Mean value for mono-culture of in dignity score
mean(mono_dig_culture)

# Mean value for bio-culture of in face score
mean(bio_face_culture)

# Mean value for bio-culture of in dignity score
mean(bio_dig_culture)
```

# (Ignore this block if not needed)
```{r}
info_ave <- Nego_data$Info_AVE
emo_ave <- Nego_data$Emotion_AVE

bio_info_ave <- c()
bio_emo_ave <- c()
mono_info_ave <- c()
mono_emo_ave <- c()

for (i in 1:length(Culture)){
  if (Culture[i] == "1"){
    mono_info_ave <- c(mono_info_ave, info_ave[i])
    mono_emo_ave <- c(mono_emo_ave, emo_ave[i])
  } else{
    bio_info_ave <- c(bio_info_ave, info_ave[i])
    bio_emo_ave <- c(bio_emo_ave, emo_ave[i])
  }
}

# Drop NA value from list
mono_emo_ave <- mono_emo_ave[-c(49, 50, 52)]
mono_info_ave <- mono_info_ave[-c(49, 50, 52)]
```

# One-way ANOVA test on informational value for 2 mono & bio groups
# One-way ANOVA test on emotional value for 2 mono & bio groups
```{r}
# one-way ANOVA info
one_way_info <- aov(info_ave ~ Culture)
summary(one_way_face)

# one-way ANOVA emo
one_way_emo <- aov(emo_ave ~ Culture)
summary(one_way_dig)
```

# Some hist plots for participants's age and gender distribution
```{r}
dignity <- c()
bio <- c()
info_dignity <- c()
info_bio <- c()
emo_dignity <- c()
emo_bio <- c()

par(mfrow = c(1, 2))
for (i in 1:length(Nego_data$ResponseId)){
  if (Nego_data$Bio_Culture[i] < 2){
    dignity <- c(dignity, Nego_data$Age[i])
    info_dignity <- c(info_dignity, Nego_data$Info_AVE[i])
    emo_dignity <- c(emo_dignity, Nego_data$Emotion_AVE[i])
  }
  else{
    bio <- c(bio, Nego_data$Age[i])
    info_bio <- c(info_bio, Nego_data$Info_AVE[i])
    emo_bio <- c(emo_bio, Nego_data$Emotion_AVE[i])
  }
}

hist(dignity)
hist(bio)
hist(info_dignity)
hist(info_bio)
hist(emo_dignity)
hist(emo_bio)
hist(Nego_data$Gender)
```
